Ice-shelf ocean boundary layer dynamics from large-eddy simulations

### 2021-10-19 Response_reviewers_rev1.tex

Major points:\vspace{12pt}

Section 2.3: Please add the figure illustrating simulation setup for your base case. Add more detail in this figure: currently even the sizes of the domain are not written anywhere.\\
\textit{We have added a schematic figure (Figure 1). This text specifying the domain size was included in the original manuscript, but it would be easy to miss. With the new figure, it should be more visible}
\begin{quote}
``The domain is a 64 m$^3$ cube''
\end{quote}\vspace{12pt}

L 100: please add more detail about validation in the appendix. It would be useful to have an idea how the chosen model works compared to other model (which one? Was it DNS or measurements or another LES model?).\\
\textit{We have added a figure to the supplemental materials (Figure S1) and the following text to the manuscript. We don't feel that too much information is needed about model set-up because we follow Abkar and Moin (2017) exactly.}
\begin{quote}
``We validated our implementation against the stable atmospheric boundary layer test case published in \citet{abkar_large-eddy_2017} and \citet{stoll_large-eddy_2008}. We follow \citet[]['s]{abkar_large-eddy_2017}'s model set-up exactly and chose their moderate resolution with 72x72x72 grid points. Our results are in good agreement with \citet[]['s]{abkar_large-eddy_2017} solution employing another LES model with AMD (boundary layer height differs by <10\%) and other LES models with different turbulence closures (Fig. S1, their Fig. 1 and references therein).''
\end{quote}\vspace{12pt}

L 150: How does the resolution influence the results? Why this particular resolution was chosen?
\textit{We chose this resolution as the highest we could afford for this parameter study while achieving similar behavior to higher resolution simulations. We conducted one simulation at twice the resolution and compared the results, now described in the following text and a supplemental figure.}
\begin{quote}
``We evaluated the effects of doubling both horizontal and vertical resolution in a separate simulation with an otherwise identical set-up to the base case, run for one inertial period after spin-up. While a greater portion of the vertical heat fluxes was resolved as expected, the melt rate averaged over one inertial period only increased by 7\% and differences in the mean state were sufficiently small to justify the use of our standard resolution (Figure~S2).''
\end{quote}
\vspace{12pt}

@@

Why the form with power ‘-1’ is chosen if that power can be removed from this equation. In addition, I have not found this or similar expression in McPhee et al (1987), please clarify.\\
\textit{The power of -1 was not necessary in these equations an has been removed. This form (without the -1 power) can be found in Equation 11 of McPhee et al. (1987) where the second term is the molecular contribution.}\vspace{12pt}

Eq (14) $c_p$ should be removed, it makes the expression dimensionally inconsistent.\\
\textit{Change has been made.}\vspace{12pt}

L 146: ‘It is noted by the PALM developers that this error was found to be small’ –please provide a reference here.\\
\textit{This note is embedded in the code itself.}
\url{https://github.com/lanl/palm_lanl/blob/7f1444073b20ae81b451d4ab469d13e66b5358b7/trunk/SOURCE/surface_layer_fluxes_mod.f90#L2513-L2519}\vspace{12pt}

L 168: far field thermal driving is 0.15C, but in the figures elsewhere, there is no such case, only 0.1C. I believe one of those is a misprint.
It was actually the legend of these figures that was not shown with sufficient precision. We have increased the precision such that the 0.15C case is labeled appropriately in all figures.
\vspace{12pt}

@@

L 147: ‘This error would be small if the first ∼10 cm were largely a constant flux layer, as hypothesized by McPhee (1983).’ – I do not understand this sentence. Clearly, if 10 cm were a constant flux layer, then the mentioned fluxes would be equal. What was hypothesized by McPhee?\\
\textit{We have edited the text to be a bit more specific about what we mean. We hoped to convey that the surface layer is thought to deviate only slightly from a constant flux layer. We also changed the citation to McPhee (1981), which contains this argument in more detail (though the 1983 paper provides the extension to scalar fluxes).}
\begin{quote}
``This error would be small if the first $\sim$10\,\unit{cm} were nearly a constant flux layer; \citet{mcphee_analytic_1981} hypothesized that the sub-ice surface layer would be nearly but not exactly a constant flux layer.''
\end{quote}\vspace{12pt}

L 205: ‘thermal driving increases from 0.5 to 0.6C ’: there is no 0.5C case in the figure.
\textit{We have corrected this typo to refer to the 0.4C thermal driving case.}
\vspace{12pt}
